Dynamic Grammars for Embedded ASR

### 2019-01-05 2019-cicling-la-rochelle/kmgram.tex
wip: cicling 2019

As a compromise, we have chosen the excellent free software speech recognition
tool Julius\cite{lee2001julius}, \cite{lee2009recent}, which is very stable,
feature-rich and allows HMM as well as GMM-DNN-hybrid models.

@@

\begin{thebibliography}{}

\end{thebibliography}
%\bibliography{paper}
\end{document}

>>>>

As a compromise, we have chosen the excellent free software speech recognition
tool Julius\cite{lee2001julius}, \cite{lee2009recent}, which is very mature,
feature-rich and allows HMM as well as DNN and GMM-DNN-hybrid models.

\subsection{Acoustic Modeling}

We have used the Mozilla Common Voice\footnote{voice.mozilla.org} corpus for
training, the CMU Sphinx\cite{lamere2003cmu} dictionary and their
Tensorflow\cite{abadi2016tensorflow}-based pronunciation tool named {\em
g2p-seq2seq} for phonetic transcription. For training of the models, we have
used HTK\cite{young2002htk}. We use tied-state triphones clustered by decision
trees and Gaussian mixture models with 8 mixtures.

The model in binary form has 23MB and takes about 2 seconds to load on the
device.

\subsection{Usage}

The glass runs dedicated applications to perform its various tasks. All of those
applications are designed to be controlled by four directional arrow keys and a
confirm key. The remaining four keys present on the control box are for
operations outside the scope of an application. For example, turning the display
on and off, exiting to the main screen etc.

By default, the voice control uses a grammar that copies the buttons, i.e. it is
in an isolated-word mode with vocabulary of {\em next, back, up, down, OK}.
Some synonyms are also recognized, like {\em left} for {\em back}, {\em upward}
for {\em up} or {\em enter} for {\em OK}.

Whenever one of these commands is recognized, pressing the corresponding key
is triggered.

Every application can either rely on this behavior or capture the recognition
output, handling it as it sees fit. The recognition grammar can be redefined, so
the set of commands is changed as long as the app is running.

For example, an application that offers a list of items for selection, can
define the recognition grammar to accept commands {\em next}, {\em back}, {\em
OK} and the names of the offered items. Of course, this requires that the
pronounciation of each item is known. We do not run g2p-seq2seq on the device
for performance reasons, so this has to be taken care of in advance.

\section{Architecture}

The glass uses the web platform internally. Firefox (version 52) serves web applications
locally via the \texttt{file://} protocol. There is a Java-based middleware
layer called the SG server, which provides endpoints for camera, logs and other
device functionality. Julius can run either as a command-line application
outputting to standard output, or as a TCP server capable of handling one single
connection at a time.

The browser supports websockets, which is the most suitable technology for
accepting a continuous data stream over extended time periods without the
necessity of polling on the client side. To bridge the
websocket-protocol-speaking client with the TCP-speaking server, and to mitigate
the limitation to a single connection, we have created a {\em broker}

@@

\bibliography{citace}

\end{document}
